#### Exercise 3: House Prices

In this exercise, you will work with the [house prices dataset obtained from Kaggle](https://www.kaggle.com/c/house-prices-advanced-regression-techniques/data).
The dataset contains 81 columns describing (almost) every aspect of residential homes in Ames, Iowa.

__3.a__ Save the [data file](https://raw.githubusercontent.com/tvatter/dsfba_2019/homework/data/house_prices.csv) in `data` folder of your project. Load the dataset into the global environment by using function `read_csv` and assign it to variable `house_prices`. Make sure that the class of `house_prices` is a tibble.

```{r, message = FALSE}

### your code goes here

```

__3.b__ You will work with only four variables, namely, `LotArea`, `KitchenQual`, `LotShape`, and `SalePrice`, which indicate area (in square feet), kitchen quality, general shape, and sale price (in dollars) of property. 
Modify `house_prices` to have only these four columns, as well as transform `LotArea` from square feet into square meters. Bonus: try to use only one `dplyr` function.

```{r, message = FALSE}

### your code goes here

```

__3.c__ For how many lots have the sale price was greater than its mean value?

```{r, message = FALSE}

### your code goes here

```


__3.d__ Display the average sale price for each kitchen quality level.

  Note, levels of `KitchenQual` correspond to the followin values:

    - Ex -- Excellent,
    - Gd -- Good,
    - TA -- Typical/Average,
    - Fa -- Fair
    - Po -- Poor

```{r, message = FALSE}

### your code goes here

```

__3.e__ Display ten randomly selected observations from the dataset. What happens if you execute your code a few times? How can you make sure that each execution returns the exact 10 rows?

```{r, message = FALSE}

### your code goes here

```

__3.f__ Print out the minimum price of observations for which shape is regular (i.e., `"Reg"`), and the kitchen has excellent quality.

```{r, message = FALSE}

### your code goes here

  
```

__3.g__ Produce boxplots with kitchen quality as the x-axis and the price as the y-axis. Regroup kitchen quality in the following order: excellent, good, typical/average, and fair. What can you say about the relationship between kitchen quality and the price?

```{r, message = FALSE}

### your code goes here

```

__3.h__ Draw a scatter chart to investigate the dependence between `LotArea` and `SalePrice`. Further, use different colors depending on the kitchen quality, and different shapes depending on the shape of the property. 

```{r, message = FALSE}

### your code goes here


```
